partial: An R Package for Creating Partial Dependence Plots

### 2016-08-09 manuscript/greenwell.tex
minor edits

Currently, only two functions are exported by \pkg{partial}:
\begin{itemize}
  \item \code{partial}
  \item \code{plotPartial}
\end{itemize}
The \code{partial} function evaluates the partial dependence \eqref{eqn:pdf} from a fitted model over a grid of predictor values. If \code{plot = FALSE} (the default), \code{partial} returns a data frame with an additional class: \code{"partial"}. The columns are labeled in the same order as the features supplied to \code{pred.var}, and the last column is always labeled \code{y} and contains the partial dependence function values $\bar{f}_s\left(\boldsymbol{z}_s\right)$. If \code{plot = TRUE}, then \code{partial} returns a \CRANpkg{lattice} plot \citep{lattice-pkg}. For more advanced plotting, the \code{plotPartial} function will take a \code{"partial"} object and display a more customizable lattice plot. Currently supported models are described in Table~\ref{tab:models}.
\begin{table}[htbp]
  \begin{tabular}{p{4cm}ll}
    \toprule
      Model & Package & Class \\
      \midrule
      Bagged decision trees     & \CRANpkg{ipred} \citep{ipred-pkg} & \code{"classbagg"}, \code{"regbagg"} \\
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"bagging"} \\
      Boosted decision trees    & \pkg{gbm}      & \code{"gbm"} \\
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"boosting"} \\
      Conditional random forest & \pkg{party}    & \code{"RandomForest"} \\
                                & \pkg{partykit} & \code{"cforest"} \\
      Decision trees            & \CRANpkg{rpart} \citep{rpart-pkg} & \code{"rpart"} \\
                                & \pkg{party}    & \code{"BinaryTree"} \\
                                & \pkg{partykit} & \code{"constparty"}/\code{"party"} \\
      Linear model              & \pkg{stats}    & \code{"lm"} \\
      Multivariate adaptive regression splines (MARS) & \CRANpkg{earth} \citep{earth-pkg} & \code{"earth"} \\
      Random forest & \pkg{randomForest} & \code{"randomForest"} \\
      Support vector machines & \CRANpkg{e1071} \citep{e1071-pkg} & \code{"svm"} \\
                              & \CRANpkg{kernlab} \citep{kernlab-pkg} & \code{"ksvm"} \\
      \bottomrule
  \end{tabular}
  \caption{Models specifically supported by the \pkg{package}.}
  \label{tab:models}
\end{table}
The \code{partial.default} method should be able to handle most other types of models not listed in Table~\ref{tab:models}; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} or projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package.

>>>>

Currently, only two functions are exported by \pkg{partial}:
\begin{itemize}
  \item \code{partial}
  \item \code{plotPartial}
\end{itemize}
The \code{partial} function evaluates the partial dependence \eqref{eqn:pdf} from a fitted model over a grid of predictor values. If \code{plot = FALSE} (the default), \code{partial} returns a data frame with an additional class: \code{"partial"}. The columns are labeled in the same order as the features supplied to \code{pred.var}, and the last column is always labeled \code{y} and contains the partial dependence function values $\bar{f}_s\left(\boldsymbol{z}_s\right)$. If \code{plot = TRUE}, then \code{partial} returns a \CRANpkg{lattice} plot \citep{lattice-pkg}. For more advanced plotting, the \code{plotPartial} function will take a \code{"partial"} object and display a more customizable lattice plot.

Currently supported models are described in Table~\ref{tab:models}. The \code{partial.default} method, however, should be able to handle most other types of models; for example, neural networks from the \CRANpkg{nnet} package \citep{venables-modern-2002} or projection pursuit regression \citep{friedman-ppr-1981} using the \code{ppr} function in the \pkg{stats} package.
\begin{table}[htbp]
  \begin{tabular}{p{4cm}ll}
    \toprule
      Model & Package & Class \\
      \midrule
      Bagged decision trees     & \CRANpkg{ipred} \citep{ipred-pkg} & \code{"classbagg"}, \code{"regbagg"} \\
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"bagging"} \\
      Boosted decision trees    & \pkg{gbm}      & \code{"gbm"} \\
                                & \CRANpkg{adabag} \citep{adabag-pkg} & \code{"boosting"} \\
      Conditional random forest & \pkg{party}    & \code{"RandomForest"} \\
                                & \pkg{partykit} & \code{"cforest"} \\
      Decision trees            & \CRANpkg{rpart} \citep{rpart-pkg} & \code{"rpart"} \\
                                & \pkg{party}    & \code{"BinaryTree"} \\
                                & \pkg{partykit} & \code{"constparty"}/\code{"party"} \\
      Linear model              & \pkg{stats}    & \code{"lm"} \\
      Multivariate adaptive regression splines (MARS) & \CRANpkg{earth} \citep{earth-pkg} & \code{"earth"} \\
      Random forest & \pkg{randomForest} & \code{"randomForest"} \\
      Support vector machines & \CRANpkg{e1071} \citep{e1071-pkg} & \code{"svm"} \\
                              & \CRANpkg{kernlab} \citep{kernlab-pkg} & \code{"ksvm"} \\
      \bottomrule
  \end{tabular}
  \caption{Models specifically supported by the \pkg{package}.}
  \label{tab:models}
\end{table}
